### 2022-02-13 src/text/2-package-subsections/makers.tex

Finally, to limit other sources of systematic uncertainties, a data validity domain is
determined by the \texttt{SafeMaskMaker}. It can be used to limit the extent of the field
of view used or to limit the energy range to e.g. a domain where the energy reconstruction
bias is below a given value.

>>>>

Finally, to limit other sources of systematic uncertainties, a data validity domain is
determined by the \texttt{SafeMaskMaker}. It can be used to limit the extent of the field
of view used or to limit the energy range to e.g., a domain where the energy reconstruction
bias is below a given value.
